---
title: "Dynamic Ecology Email Poll Results"
author: "Meghan Duffy"
date: "November 6, 2016"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", error = TRUE)
```

# Analysis of poll asking Dynamic Ecology readers about their email
Poll appeared October 24, 2016 and closed on November 6, 2016
Poll available at:
https://dynamicecology.wordpress.com/2016/10/24/how-do-you-manage-email/

## First, more about the poll and responses
Poll received just over 417 responses. One of these was completely blank, so I deleted it, leaving 416. 

### Q1: How many work-related emails are in your inbox now?
```
1 = Inbox zero!!!
2 = < 20
3 = 20-50
4 = 50-100
5 = 100-500
6 = > 500
```

### Q2: What is your goal for the number of work-related emails you aim have in your inbox?
```
1 = Inbox zero!!!
2 = < 20
3 = 20-50
4 = 50-100
5 = 100-500
6 = > 500
7 = I don't care how many emails are in my inbox
```

### Q3: How often do you feel overwhelmed by email?
```
1 = never
2 = rarely
3 = sometimes
4 = most of the time
5 = always
```

### Q4: Which of the following best describes your current position?
```
1 = Undergrad student
2 = Grad student
3 = Postdoc
4 = Research scientist in academia
5 = Assistant professor
6 = Associate professor
7 = Full professor
8 = Technician
9 = Research scientist in industry
10 = Research scientist in government
11 = Scientist at an NGO/non-profit
12 = Other government position
13 = Other
```

### Q5: How old are you?
```
1 = <25
2 = 25-34
3 = 35-44
4 = 45-54
5 = 55-64
6 = >65-74
7 = >75
```

## Results

```{r,load libraries,message=FALSE,echo=FALSE}
library(ggplot2)
library(dplyr)
library(cowplot)
```

```{r, read in data}
emaildata <- read.csv("DynamicEcologyemailquiz.csv", na.strings = ".")
head(emaildata)
str(emaildata)
```

