---
title: "Dynamic Ecology Email Poll Results"
author: "Meghan Duffy"
date: "November 6, 2016"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", error = TRUE)
```

# Analysis of poll asking Dynamic Ecology readers about their email
Poll appeared October 24, 2016 and closed on November 6, 2016
Poll available at:
https://dynamicecology.wordpress.com/2016/10/24/how-do-you-manage-email/

## First, more about the poll and responses
Poll received just over 417 responses. One of these was completely blank, so I deleted it, leaving 416. 

### Q1: How many work-related emails are in your inbox now?
```
1 = Inbox zero!!!
2 = < 20
3 = 20-50
4 = 50-100
5 = 100-500
6 = > 500
```

### Q2: What is your goal for the number of work-related emails you aim have in your inbox?
```
1 = Inbox zero!!!
2 = < 20
3 = 20-50
4 = 50-100
5 = 100-500
6 = > 500
7 = I don't care how many emails are in my inbox
```

### Q3: How often do you feel overwhelmed by email?
```
1 = never
2 = rarely
3 = sometimes
4 = most of the time
5 = always
```

### Q4: Which of the following best describes your current position?
```
1 = Undergrad student
2 = Grad student
3 = Postdoc
4 = Research scientist in academia
5 = Assistant professor
6 = Associate professor
7 = Full professor
8 = Technician
9 = Research scientist in industry
10 = Research scientist in government
11 = Scientist at an NGO/non-profit
12 = Other government position
13 = Other
```

### Q5: How old are you?
```
1 = <25
2 = 25-34
3 = 35-44
4 = 45-54
5 = 55-64
6 = >65-74
7 = >75
```

## Results

```{r,load libraries,message=FALSE,echo=FALSE}
library(ggplot2)
library(dplyr)
library(cowplot)
require(likert)
```

```{r, read in data}
emaildata <- read.csv("DynamicEcologyemailquiz.csv", na.strings = ".")
head(emaildata)
str(emaildata)
```

```{r, summarize current inbox status}
CurrentSum <- 
  emaildata %>%
  filter(!is.na(CurrentEmails01)) %>%
  group_by(CurrentEmails01) %>%
  summarise(n=n()) %>%
  mutate(rel.freq = round(100 * n/sum(n), 0))

CurrentSum

as.factor(CurrentSum$CurrentEmails01)

currentemailplot <- ggplot(CurrentSum,aes(x=CurrentEmails01,y=rel.freq)) +
  geom_bar(stat="identity") +
  ylab("Percent of responses") +
  theme(legend.position="none") +
  coord_flip() +
  theme(axis.text.y = element_blank()) +
  annotate("text", x = 1, y = 1, label = "Inbox zero!!!", hjust=0, size=6, color = "white") +
  annotate("text", x = 2, y = 1, label = "< 20", hjust=0, size=6, color = "white") +
  annotate("text", x = 3, y = 1, label = "20-50", hjust=0, size=6, color = "white") +
  annotate("text", x = 4, y = 1, label = "50-100", hjust=0, size=6, color = "white") +
  annotate("text", x = 5, y = 1, label = "100-500", hjust=0, size=6, color = "white") +
  annotate("text", x = 6, y = 1, label = "> 500", hjust=0, size=6, color = "white") +
  ggtitle("How many work-related emails are in your inbox now?") +
  theme(plot.title=element_text(size=12)) +
  theme(axis.title.y=element_blank()) +
  theme(axis.title.x=element_text(size=12)) +
  theme(axis.ticks.y = element_blank())

save_plot("currentemailplot.jpg", currentemailplot)

currentemailplot
```

```{r, summarize target inbox status}
TargetSum <- 
  emaildata %>%
  filter(!is.na(TargetEmails01)) %>%
  group_by(TargetEmails01) %>%
  summarise(n=n()) %>%
  mutate(rel.freq = round(100 * n/sum(n), 0))

TargetSum

as.factor(TargetSum$TargetEmails01)

targetemailplot <- ggplot(TargetSum,aes(x=TargetEmails01,y=rel.freq)) +
  geom_bar(stat="identity") +
  ylab("Percent of responses") +
  theme(legend.position="none") +
  coord_flip() +
  theme(axis.text.y = element_blank()) +
  annotate("text", x = 1, y = 1, label = "Inbox zero!!!", hjust=0, size=6, color = "white") +
  annotate("text", x = 2, y = 1, label = "< 20", hjust=0, size=6, color = "white") +
  annotate("text", x = 3, y = 1, label = "20-50", hjust=0, size=6, color = "white") +
  annotate("text", x = 4, y = 4, label = "50-100", hjust=0, size=6, color = "black") +
  annotate("text", x = 5, y = 4, label = "100-500", hjust=0, size=6, color = "black") +
  annotate("text", x = 6, y = 4, label = "> 500", hjust=0, size=6, color = "black") + 
  annotate("text", x = 7, y = 1, label = "I don't care", hjust=0, size=6, color = "white") +
  ggtitle("What is your goal for the number of work-related \nemails you aim have in your inbox?") +
  theme(plot.title=element_text(size=12)) +
  theme(axis.title.y=element_blank()) +
  theme(axis.title.x=element_text(size=12)) +
  theme(axis.ticks.y = element_blank())

save_plot("targetemailplot.jpg", targetemailplot)

currentemailplot
```

```{r, summarize overwhelmed status}
OverwhelmedSum <- 
  emaildata %>%
  filter(!is.na(Overwhelmed01)) %>%
  group_by(Overwhelmed01) %>%
  summarise(n=n()) %>%
  mutate(rel.freq = round(100 * n/sum(n), 0))

OverwhelmedSum

as.factor(OverwhelmedSum$Overwhelmed01)

overwhelmedplot <- ggplot(OverwhelmedSum,aes(x=Overwhelmed01,y=rel.freq)) +
  geom_bar(stat="identity") +
  ylab("Percent of responses") +
  theme(legend.position="none") +
  coord_flip() +
  theme(axis.text.y = element_blank()) +
  annotate("text", x = 1, y = 3, label = "never", hjust=0, size=6, color = "black") +
  annotate("text", x = 2, y = 1, label = "rarely", hjust=0, size=6, color = "white") +
  annotate("text", x = 3, y = 1, label = "sometimes", hjust=0, size=6, color = "white") +
  annotate("text", x = 4, y = 1, label = "most of the time", hjust=0, size=6, color = "white") +
  annotate("text", x = 5, y = 1, label = "always", hjust=0, size=6, color = "white") +
  ggtitle("How often do you feel overwhelmed by email?") +
  theme(plot.title=element_text(size=12)) +
  theme(axis.title.y=element_blank()) +
  theme(axis.title.x=element_text(size=12)) +
  theme(axis.ticks.y = element_blank())

save_plot("overwhelmedplot.jpg", overwhelmedplot)

overwhelmedplot
```

Now that basic results are plotted, moving on to some more interesting things. First, some cross tabs:
```{r, cross tabs}
xtabs(~CurrentEmails+CurrentPosition,data=emaildata)
xtabs(~Overwhelmed+CurrentPosition,data=emaildata)
xtabs(~TargetEmails+CurrentPosition,data=emaildata)
```

Now, using the Likert package:
```{R, Likert cross tabs on current email data}
## first, subsetting the data to grad students, postdocs, asst/assoc/full profs
academicpathdata <- subset(emaildata, CurrentPosition == "Grad student" | CurrentPosition == "Postdoc" | CurrentPosition == "Assistant professor" | CurrentPosition == "Associate professor" | CurrentPosition == "Full professor")

currentdata <-
  academicpathdata %>%
  filter(CurrentEmails01 != "NA", TargetEmails01 != "NA", 
         Overwhelmed01 != "NA", Age01 != "NA") %>% 
  select(CurrentEmails)

# order the data
currentdata$CurrentEmails <- factor(currentdata$CurrentEmails, 
                                      c("Inbox zero!!!",
                                        "<20",
                                        "20-50",
                                        "50-100",
                                        "100-500",
                                        ">500"))

# changing the column name to the question
colnames(currentdata)[1] <- "How many work-related emails are in your inbox now?"

## subsetting the likert data AND the grouping variables
currentdata_grouping <-
  academicpathdata %>%
  filter(CurrentEmails01 != "NA", TargetEmails01 != "NA", 
         Overwhelmed01 != "NA", Age01 != "NA") %>%
  select(TargetEmails, Overwhelmed, CurrentPosition, Age) 

currentdata_grouping$TargetEmails <- factor(currentdata_grouping$TargetEmails, 
                                            c("Inbox zero!!!", 
                                              "<20", 
                                              "20-50",
                                              "50-100",
                                              "100-500", 
                                              ">500",
                                              "I don't care how many emails are in my inbox"))

currentdata_grouping$Overwhelmed <- factor(currentdata_grouping$Overwhelmed, 
                                            c("Never", 
                                              "Rarely", 
                                              "Sometimes",
                                              "Most of the time",
                                              "Always"))

currentdata_grouping$CurrentPosition <- factor(currentdata_grouping$CurrentPosition, 
                                            c("Grad student", 
                                              "Postdoc",
                                              "Assistant professor",
                                              "Associate professor",
                                              "Full professor"))

likert_11 <- likert(currentdata, grouping = currentdata_grouping$CurrentPosition)
plot(likert_11)
```

```{R, Likert cross tabs on target email data}
targetdata <-
  academicpathdata %>%
  filter(CurrentEmails01 != "NA", TargetEmails01 != "NA", 
         Overwhelmed01 != "NA", Age01 != "NA") %>% 
  select(TargetEmails)

# order the data
targetdata$TargetEmails <- factor(targetdata$TargetEmails, 
                                      c("Inbox zero!!!",
                                        "<20",
                                        "20-50",
                                        "50-100",
                                        "100-500",
                                        ">500",
                                        "I don't care how many emails are in my inbox"))

# changing the column name to the question
colnames(targetdata)[1] <- "What is your goal for the number of work-related emails you aim have in your inbox?"

## subsetting the likert data AND the grouping variables
targetdata_grouping <-
  academicpathdata %>%
  filter(CurrentEmails01 != "NA", TargetEmails01 != "NA", 
         Overwhelmed01 != "NA", Age01 != "NA") %>%
  select(CurrentEmails, Overwhelmed, CurrentPosition, Age) 

targetdata_grouping$CurrentEmails <- factor(targetdata_grouping$CurrentEmails, 
                                            c("Inbox zero!!!", 
                                              "<20", 
                                              "20-50",
                                              "50-100",
                                              "100-500", 
                                              ">500"))

targetdata_grouping$Overwhelmed <- factor(targetdata_grouping$Overwhelmed, 
                                            c("Never", 
                                              "Rarely", 
                                              "Sometimes",
                                              "Most of the time",
                                              "Always"))

targetdata_grouping$CurrentPosition <- factor(targetdata_grouping$CurrentPosition, 
                                            c("Grad student", 
                                              "Postdoc",
                                              "Assistant professor",
                                              "Associate professor",
                                              "Full professor"))

likert_21 <- likert(targetdata, grouping = targetdata_grouping$CurrentPosition)
plot(likert_21)
```

```{r, Likert analysis of overwhelmed question}
overwhelmeddata <-
  academicpathdata %>%
  filter(CurrentEmails01 != "NA", TargetEmails01 != "NA", 
         Overwhelmed01 != "NA", Age01 != "NA") %>% 
  select(Overwhelmed)

# order the data
overwhelmeddata$Overwhelmed <- factor(overwhelmeddata$Overwhelmed, 
                                      c("Never", 
                                        "Rarely", 
                                        "Sometimes",
                                        "Most of the time",
                                        "Always"))

# changing the column name to the question
colnames(overwhelmeddata)[1] <- "How often do you feel overwhelmed by email?"

## subsetting the likert data AND the grouping variables

overwhelmeddata_grouping <-
  academicpathdata %>%
  filter(CurrentEmails01 != "NA", TargetEmails01 != "NA", 
         Overwhelmed01 != "NA", Age01 != "NA") %>%
  select(CurrentEmails, TargetEmails, CurrentPosition, Age) 

overwhelmeddata_grouping$CurrentEmails <- factor(overwhelmeddata_grouping$CurrentEmails, 
                                            c("Inbox zero!!!", 
                                              "<20", 
                                              "20-50",
                                              "50-100",
                                              "100-500", 
                                              ">500"))
overwhelmeddata_grouping$TargetEmails <- factor(overwhelmeddata_grouping$TargetEmails, 
                                            c("Inbox zero!!!", 
                                              "<20", 
                                              "20-50",
                                              "50-100",
                                              "100-500", 
                                              ">500",
                                              "I don't care how many emails are in my inbox"))

overwhelmeddata_grouping$CurrentPosition <- factor(overwhelmeddata_grouping$CurrentPosition, 
                                            c("Grad student", 
                                              "Postdoc",
                                              "Assistant professor",
                                              "Associate professor",
                                              "Full professor"))

likert_31 <- likert(overwhelmeddata, grouping = overwhelmeddata_grouping$CurrentPosition)
plot(likert_31)
```