---
title: "Dynamic Ecology Email Poll Results"
author: "Meghan Duffy"
date: "November 6, 2016"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", error = TRUE)
```

# Analysis of poll asking Dynamic Ecology readers about their email
Poll appeared October 24, 2016 and closed on November 6, 2016
Poll available at:
https://dynamicecology.wordpress.com/2016/10/24/how-do-you-manage-email/

## First, more about the poll and responses
Poll received just over 417 responses. One of these was completely blank, so I deleted it, leaving 416. 

### Q1: How many work-related emails are in your inbox now?
```
1 = Inbox zero!!!
2 = < 20
3 = 20-50
4 = 50-100
5 = 100-500
6 = > 500
```

### Q2: What is your goal for the number of work-related emails you aim have in your inbox?
```
1 = Inbox zero!!!
2 = < 20
3 = 20-50
4 = 50-100
5 = 100-500
6 = > 500
7 = I don't care how many emails are in my inbox
```

### Q3: How often do you feel overwhelmed by email?
```
1 = never
2 = rarely
3 = sometimes
4 = most of the time
5 = always
```

### Q4: Which of the following best describes your current position?
```
1 = Undergrad student
2 = Grad student
3 = Postdoc
4 = Research scientist in academia
5 = Assistant professor
6 = Associate professor
7 = Full professor
8 = Technician
9 = Research scientist in industry
10 = Research scientist in government
11 = Scientist at an NGO/non-profit
12 = Other government position
13 = Other
```

### Q5: How old are you?
```
1 = <25
2 = 25-34
3 = 35-44
4 = 45-54
5 = 55-64
6 = >65-74
7 = >75
```

## Results

```{r,load libraries,message=FALSE,echo=FALSE}
library(ggplot2)
library(dplyr)
library(cowplot)
require(likert)
```

```{r, read in data}
emaildata <- read.csv("DynamicEcologyemailquiz.csv", na.strings = ".")
head(emaildata)
str(emaildata)
```

```{r, summarize current inbox status}
CurrentSum <- 
  emaildata %>%
  filter(!is.na(CurrentEmails01)) %>%
  group_by(CurrentEmails01) %>%
  summarise(n=n()) %>%
  mutate(rel.freq = round(100 * n/sum(n), 0))

CurrentSum

as.factor(CurrentSum$CurrentEmails01)

currentemailplot <- ggplot(CurrentSum,aes(x=CurrentEmails01,y=rel.freq)) +
  geom_bar(stat="identity") +
  ylab("Percent of responses") +
  theme(legend.position="none") +
  coord_flip() +
  theme(axis.text.y = element_blank()) +
  annotate("text", x = 1, y = 1, label = "Inbox zero!!!", hjust=0, size=6, color = "white") +
  annotate("text", x = 2, y = 1, label = "< 20", hjust=0, size=6, color = "white") +
  annotate("text", x = 3, y = 1, label = "20-50", hjust=0, size=6, color = "white") +
  annotate("text", x = 4, y = 1, label = "50-100", hjust=0, size=6, color = "white") +
  annotate("text", x = 5, y = 1, label = "100-500", hjust=0, size=6, color = "white") +
  annotate("text", x = 6, y = 1, label = "> 500", hjust=0, size=6, color = "white") +
  ggtitle("How many work-related emails are in your inbox now?") +
  theme(plot.title=element_text(size=12)) +
  theme(axis.title.y=element_blank()) +
  theme(axis.title.x=element_text(size=12)) +
  theme(axis.ticks.y = element_blank())

save_plot("currentemailplot.jpg", currentemailplot)

currentemailplot
```

```{r, summarize target inbox status}
TargetSum <- 
  emaildata %>%
  filter(!is.na(TargetEmails01)) %>%
  group_by(TargetEmails01) %>%
  summarise(n=n()) %>%
  mutate(rel.freq = round(100 * n/sum(n), 0))

TargetSum

as.factor(TargetSum$TargetEmails01)

targetemailplot <- ggplot(TargetSum,aes(x=TargetEmails01,y=rel.freq)) +
  geom_bar(stat="identity") +
  ylab("Percent of responses") +
  theme(legend.position="none") +
  coord_flip() +
  theme(axis.text.y = element_blank()) +
  annotate("text", x = 1, y = 1, label = "Inbox zero!!!", hjust=0, size=6, color = "white") +
  annotate("text", x = 2, y = 1, label = "< 20", hjust=0, size=6, color = "white") +
  annotate("text", x = 3, y = 1, label = "20-50", hjust=0, size=6, color = "white") +
  annotate("text", x = 4, y = 4, label = "50-100", hjust=0, size=6, color = "black") +
  annotate("text", x = 5, y = 4, label = "100-500", hjust=0, size=6, color = "black") +
  annotate("text", x = 6, y = 4, label = "> 500", hjust=0, size=6, color = "black") + 
  annotate("text", x = 7, y = 1, label = "I don't care", hjust=0, size=6, color = "white") +
  ggtitle("What is your goal for the number of work-related \nemails you aim have in your inbox?") +
  theme(plot.title=element_text(size=12)) +
  theme(axis.title.y=element_blank()) +
  theme(axis.title.x=element_text(size=12)) +
  theme(axis.ticks.y = element_blank())

save_plot("targetemailplot.jpg", targetemailplot)

currentemailplot
```

```{r, summarize overwhelmed status}
OverwhelmedSum <- 
  emaildata %>%
  filter(!is.na(Overwhelmed01)) %>%
  group_by(Overwhelmed01) %>%
  summarise(n=n()) %>%
  mutate(rel.freq = round(100 * n/sum(n), 0))

OverwhelmedSum

as.factor(OverwhelmedSum$Overwhelmed01)

overwhelmedplot <- ggplot(OverwhelmedSum,aes(x=Overwhelmed01,y=rel.freq)) +
  geom_bar(stat="identity") +
  ylab("Percent of responses") +
  theme(legend.position="none") +
  coord_flip() +
  theme(axis.text.y = element_blank()) +
  annotate("text", x = 1, y = 3, label = "never", hjust=0, size=6, color = "black") +
  annotate("text", x = 2, y = 1, label = "rarely", hjust=0, size=6, color = "white") +
  annotate("text", x = 3, y = 1, label = "sometimes", hjust=0, size=6, color = "white") +
  annotate("text", x = 4, y = 1, label = "most of the time", hjust=0, size=6, color = "white") +
  annotate("text", x = 5, y = 1, label = "always", hjust=0, size=6, color = "white") +
  ggtitle("How often do you feel overwhelmed by email?") +
  theme(plot.title=element_text(size=12)) +
  theme(axis.title.y=element_blank()) +
  theme(axis.title.x=element_text(size=12)) +
  theme(axis.ticks.y = element_blank())

save_plot("overwhelmedplot.jpg", overwhelmedplot)

overwhelmedplot
```

Now that basic results are plotted, plan to do Likert analyses, similar to ones done here:
https://github.com/duffymeg/DEAuthorshipPoll/blob/master/AuthorshipPollAnalysis.Rmd
